### 2023-07-17 CV2/general.tex
-

\section{Positions}
\begin{tabular}{rl}	
	\textsc{2022-Now}& Postdoctoral Researcher\\
	& \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Université catholique de Louvain}}, Louvain-la-Neuve, Belgium\\
	\textsc{2022}& Researcher\\
	&Laboratory of Advanced Combinatorics and Network Applications\\
	&\textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
	\textsc{2021-2022}& Research Intern\\
	 &Research Center for Trusted Artificial Intelligence\\
	 &\textbf{\href{https://www.ispras.ru/en/}{\color{black}Ivannikov Institute for System Programming}}, Moscow, Russia
\end{tabular}

@@

\begin{tabular}{rl}
	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures, JAX, PyTorch\\
	& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, DirectX, Vulkan, HTML/CSS\\
	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
	\textsc{Computer} & macOS, LaTeX, Git\\
%	\textsc{Languages} & English (Advanced), Russian (Native)
\end{tabular}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\section{Languages}

\begin{tabular}{rl}
	\textsc{English} & Advanced Knowledge \\
	\textsc{Russian} & Mothertongue\\
\end{tabular}

>>>>

\section{Positions}
\begin{tabular}{rl}	
	\textsc{2022-Now}& Postdoctoral Researcher\\
	& \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Université catholique de Louvain}}, Louvain-la-Neuve, Belgium\\
	\textsc{2022-2023}& Researcher\\
	&Laboratory of Advanced Combinatorics and Network Applications\\
	&\textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
	\textsc{2021-2023}& Research Intern\\
	 &Research Center for Trusted Artificial Intelligence\\
	 &\textbf{\href{https://www.ispras.ru/en/}{\color{black}Ivannikov Institute for System Programming}}, Moscow, Russia
\end{tabular}

@@

\begin{tabular}{rl}
	\textsc{Programming} & C/C++, Python,
	Algorithms and Data Structures (\href{https://codeforces.com/profile/Dakovalev1}{Codeforces master}), JAX,\\
	&PyTorch; \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, DirectX, Vulkan, HTML/CSS\\
	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
	\textsc{Computer} & macOS, LaTeX, Git\\
		\textsc{Languages} & English (Advanced), Russian (Native)
\end{tabular}

%\begin{tabular}{rl}
%	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures (\href{https://codeforces.com/profile/Dakovalev1}{Codeforces master}),\\
%	& JAX, PyTorch\\
%	& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, DirectX, Vulkan, HTML/CSS\\
%	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
%	\textsc{Computer} & macOS, LaTeX, Git\\
%	\textsc{Languages} & English (Advanced), Russian (Native)
%\end{tabular}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
%\section{Languages}
%
%\begin{tabular}{rl}
%	\textsc{English} & Advanced Knowledge \\
%	\textsc{Russian} & Mothertongue\\
%\end{tabular}
